Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages

### 2019-04-23 sattose/paper.tex
Made all todo stuff

We then filtered the corpus further to make sure we are not including any test classes or generated classes. Many Java/Maven projects use a structure where they separate the application and it's tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively). Because of this, we chose to only use projects from the corpus which use this structure (and had at least a ``/src/main/java'' folder). To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered). Of the 14.436 projects in the corpus over 3.853 remained, which is plenty for our purposes. The script to filter the corpuses in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.

@@

>>>>

We then filtered the corpus further to make sure we are not including any test classes or generated classes. Many Java/Maven projects use a structure where they separate the application and it's tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively). Because of this, we chose to only use projects from the corpus which use this structure (and had at least a ``/src/main/java'' folder). To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered, which filtered only 5 extra projects out of the corpus). Of the 14.436 projects in the corpus over 3.848 remained, which is plenty for our purposes. The script to filter the corpus in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.

@@

%TODO

\subsection{Clone instance location}
After mapping the relations between individual clones, we looked at the location of individual clone instances. A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, this claim is based on a very small dataset and a questionable way of measurement. We validated this claim over our corpus. For this, we chose the following categories:
\begin{enumerate}
  \item \textbf{Method Level:} A clone instance that does not exceed the boundaries of a single method (optionally including the declaration of the method itself).
  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class.
  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
\end{enumerate}

%TODO

\subsection{Clone instance contents}
Finally, we looked at the contents of individual clone instances: what  kind of
